---
title: "idn_failure_point"
author: " "
date: " "
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      dpi = 400)
library(tidyverse)
library(rio)
library(mgcv)
library(latex2exp)
```




###Loading data
```{r}
load(file = here::here("ss_data_all.RData"))
```


###Identify critical strain before stress fall sharply for all alloys,
```{r}

ss_dat_d <- ss_dat_all%>%
  unite("alloy_id",
        Mo:W,
        remove = FALSE)

temp <- ss_dat_d%>%
  group_by(alloy_id)%>%
  slice_head(n=1)%>%
  ungroup()%>%
  arrange(desc(Mo), desc(Nb),desc(Ta),desc(V),desc(W))

ss_dat_d <- ss_dat_d%>%
  mutate(alloy_cnt = factor(alloy_id,
                            levels = temp$alloy_id,
                            labels = 1:length(temp$alloy_id)))
```




```{r fig.width=6, fig.height=2.5}
ss_dat_d%>%
  filter(Experiment == 1)%>%
  mutate(rep =factor(rep))%>%
  filter(strain < 0.12)%>%
  ggplot(aes(x = strain,
             y =stress,
             group = rep,
             color = rep))+
  geom_line()+
  facet_wrap(~test_type)+
  theme_bw()
```


```{r}
ss_dat_t <- ss_dat_d %>%
  filter(test_type == "Tension")

max_stress_t <- ss_dat_t %>%
  group_by(alloy_id, rep)%>% 
  summarize(stress = max(stress, na.rm = TRUE))%>%
  ungroup()


failure_points_t <- ss_dat_t%>%
                      inner_join(max_stress_t, 
                                 by = c("alloy_id", "stress", "rep"))


ss_dat_c <- ss_dat_d %>%
  filter(test_type == "Compresion")

max_stress_c <- ss_dat_c %>%
  group_by(alloy_id, rep)%>% 
  summarize(stress = max(stress, na.rm = TRUE))%>%
  ungroup()


failure_points_c <- ss_dat_c%>%
                      inner_join(max_stress_c, 
                                 by = c("alloy_id","stress", "rep"))
```


```{r}
temp_dat <- ss_dat_t %>%
  filter(Experiment == 1,
         rep == 1,
         strain < 0.05)
```


<!-- ```{r} -->
<!-- library(kernlab) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- tr <- ksmooth(x = temp_dat$strain, -->
<!--            y  = temp_dat$stress, -->
<!--            kernel = "box", -->
<!--            bandwidth = 0.001) -->
<!-- ``` -->


<!-- ```{r} -->
<!-- ms <- which.max(temp_dat$stress) -->
<!-- ``` -->


<!-- ```{r} -->
<!-- temp_dat%>% -->
<!--   mutate(yp = tr$y)%>% -->
<!--   ggplot(aes(x=strain))+ -->
<!--   geom_point(aes(y = stress))+ -->
<!--   geom_line(aes(y = yp))+ -->
<!--   geom_vline(xintercept = temp_dat$strain[ms], -->
<!--              color = "red")+ -->
<!--   theme_bw() -->
<!-- ``` -->




###Joining max_strain column to the dataset,
```{r}

max_strain_t = failure_points_t%>%
                select(strain , stress, alloy_id, rep)%>%
                rename(max_strain = strain,
                       max_stress = stress)


ss_dat_t = ss_dat_t%>%
            left_join(max_strain_t, 
                      by= c("alloy_id", "rep"))
                         


max_strain_c = failure_points_c%>%
                select(strain , stress, alloy_id, rep)%>%
                rename(max_strain = strain,
                       max_stress = stress)


ss_dat_c = ss_dat_c%>%
            left_join(max_strain_c, 
                      by= c("alloy_id", "rep"))

```




###Filtering based on critical strain, scaling the strain axis 0-1 and plotting to check,

```{r fig.width=6, fig.height=3.5}
ss_dat_t_filtered = ss_dat_t %>%
                    filter(strain < max_strain | is.na(max_strain))%>%
                    group_by(alloy_id, rep)%>%
                    unite("alloy_rep_id", 
                          c("alloy_id", "rep"),
                          remove = F)%>%
                    mutate(scaled_strain = strain / max_strain,
                           scaled_stress = stress / max_stress,
                           alloy_id = factor(alloy_id),
                           rep_f = factor(rep),
                           alloy_rep_id = factor(alloy_rep_id))%>%
                    ungroup()

ss_dat_t_filtered %>%
  unite("plot_id", 
        c("alloy_id", "rep"),
        remove = F)%>%
  mutate(elements = (Mo>0) + (Nb>0) + (Ta>0) + (V>0) + (W>0),
         elements = factor(elements))%>%
  ggplot(aes(x = strain,
             y = stress,
             group = plot_id,
             color = elements))+
  geom_line(alpha = 0.5)+
  scale_color_brewer(palette = "Set1")+
  theme_bw()+
  theme(legend.position = "right")

```



```{r}

ss_dat_c_filtered = ss_dat_c %>%
                    filter(strain < max_strain | is.na(max_strain))%>%
                    group_by(alloy_id, rep)%>%
                    unite("alloy_rep_id", 
                          c("alloy_id", "rep"),
                          remove = F)%>%
                    mutate(scaled_strain = strain / max_strain,
                           scaled_stress = stress / max_stress,
                           alloy_id = factor(alloy_id),
                           rep_f = factor(rep),
                           alloy_rep_id = factor(alloy_rep_id))%>%
                    ungroup()

ss_dat_c_filtered %>%
  ggplot(aes(x = scaled_strain,
             y = scaled_stress,
             group = alloy_rep_id,
             color = alloy_id))+
  geom_line(alpha = 0.45)+
  theme_bw()+
  theme(legend.position = "none")
```

```{r}
save(ss_dat_c_filtered,
     ss_dat_t_filtered,
     file = here::here("dat_filtered.RData"))
```



## Fit models 

### Orthonormal Basis Testing

```{r}
alr_id <- levels(ss_dat_t_filtered$alloy_rep_id)

temp_dat <- ss_dat_t_filtered%>%
          filter(alloy_rep_id==alr_id[1])
```

```{r}
source(here::here("utilities.R"))
```



```{r}
mat <- fdapace::CreateBasis(4,
                            pts = temp_dat$scaled_strain,
                            type = "legendre01")

matplot(y=mat, x = temp_dat$scaled_strain,
        type = "l")

```

```{r}
mat <- create_leg_basis_fun(n_funs = 5,
                            pts = temp_dat$scaled_strain,
                            intercept = T)

matplot(y=mat, x = temp_dat$scaled_strain,
        type = "l")
```


```{r}
crossprod(mat)
```



```{r}
colnames(mat) <- paste("bf", 1:5, sep = "_")

reg_dat <- as_tibble(mat)%>%
            mutate(stress = temp_dat$stress)
```


```{r}
reg_mod <- lm(stress ~ -1 + .,
              data = reg_dat)
```

```{r}
temp_dat%>%
  mutate(pred = reg_mod$fitted.values)%>%
  ggplot(aes(x = scaled_strain))+
  geom_line(aes(y = stress),
             alpha = 0.5)+
  geom_line(aes(y = pred))+
  theme_bw()
```

```{r}
coef(reg_mod)
```

### Othonormal basis fitting


```{r}
n_f <- 4:12
dat_gcv <- vector(mode = "list",
                   length = length(n_f))
lam_v <- c(0, 1, 10)
k <- 0

for(j in 1:3){
  for(i in 1:length(n_f)){
    k <- k + 1
    dat_orth_coefs_t <- fit_leg_basis_mod_fun(ss_dat = ss_dat_t_filtered%>%
                                              mutate(scaled_stress = stress),
                                            n_funs = n_f[i],
                                            lam = lam_v[j],
                                            intercept = T)
  
    dat_orth_coefs_c <- fit_leg_basis_mod_fun(ss_dat = ss_dat_c_filtered%>%
                                                mutate(scaled_stress = stress),
                                              n_funs = n_f[i],
                                              lam = lam_v[j],
                                              intercept = T)
    
    dat_gcv[[k]] <- dat_orth_coefs_c%>%
                      mutate(Test = "Com")%>%
                      bind_rows(dat_orth_coefs_t%>%
                                  mutate(Test = "Ten"))%>%
                      filter(coef_names == "gcv")%>%
                      mutate(nb = n_f[i],
                             lam = lam_v[j])
  }
}



```

```{r}
dat_gcv <- bind_rows(dat_gcv)
```


```{r fig.width=6, fig.height=3.4}
dat_gcv_avg <- dat_gcv%>%
                group_by(nb, lam, Test)%>%
                mutate(val = mean(val))
dat_gcv%>%
  mutate(nb = factor(nb),
         lam = factor(lam))%>%
  ggplot(aes(x = nb,
             y = val,
             colour = lam))+
  geom_boxplot()+
  facet_wrap(~Test)

dat_gcv_avg%>%
  mutate(lam = factor(lam))%>%
  ggplot(aes(x = nb,
             y = val,
             colour = lam))+
  geom_line()+
  facet_wrap(~Test, scales = "free")+
  theme(legend.position = "right")
```



```{r}
dat_orth_coefs_t <- fit_leg_basis_mod_fun(ss_dat = ss_dat_t_filtered%>%
                                            mutate(scaled_stress = stress),
                                          n_funs = 4,
                                          intercept = T)
dat_orth_coefs_c <- fit_leg_basis_mod_fun(ss_dat = ss_dat_c_filtered%>%
                                              mutate(scaled_stress = stress),
                                            n_funs = 5,
                                            intercept = T)
  
dat_orth_coefs_pred_t <- fit_leg_basis_mod_fun(ss_dat = ss_dat_t_filtered%>%
                                            mutate(scaled_stress = stress),
                                          n_funs = 4,
                                          intercept = T,
                                          return_pred = T)

dat_orth_coefs_pred_c <- fit_leg_basis_mod_fun(ss_dat = ss_dat_c_filtered%>%
                                            mutate(scaled_stress = stress),
                                          n_funs = 5,
                                          intercept = T,
                                          return_pred = T)
```

```{r}
dat_pred <- bind_rows(dat_orth_coefs_pred_c$preds,
                      dat_orth_coefs_pred_t$preds)
```

```{r fig.height=4, fig.width=9}
metals <- c("Mo", "Nb", "Ta", "V","W", "Mo_Nb_Ta_V_W")
ss_dat_all%>%
  filter(alloy %in% metals,
         strain < 0.2)%>%
  mutate(alloy = factor(alloy,
                        levels = metals))%>%
  ggplot(aes(x=strain,
             y=stress,
             colour = alloy))+
  geom_line(linewidth = 1)+
  scale_color_brewer(palette =  "Paired")+
  facet_wrap(~test_type,
             scales = "free")+
  theme_bw()
```

```{r fig.height=4, fig.width=9}
metals <- c("Mo", "Nb", "Ta", "V","W", "Mo_Nb_Ta_V_W")
ss_dat_all%>%
  filter(alloy %in% metals,
         strain < 0.2)%>%
  mutate(alloy = factor(alloy,
                        levels = metals))%>%
  ggplot(aes(x=strain,
             y=stress,
             colour = alloy))+
  geom_ribbon(aes(ymax=pred_stress,
                  fill = alloy),
              ymin = 0, alpha = 0.5,
            data = dat_pred%>%
              filter(alloy %in% metals)%>%
  mutate(alloy = factor(alloy,
                        levels = metals)))+
  geom_line(linewidth = 1)+
  scale_color_brewer(palette =  "Paired")+
   scale_fill_brewer(palette =  "Paired")+
  facet_grid(test_type~alloy,
             scales = "free")+
  theme_bw()
```

```{r}
dat_alloy <- ss_dat_c_filtered%>%
                          arrange(alloy_rep_id)%>%
                          group_by(alloy_rep_id)%>%
                          slice_head(n=1)%>%
            ungroup()%>%
            select(alloy_rep_id,alloy,Mo,Nb,Ta,V,W, rep, Experiment, alloy_cnt)
```



```{r  fig.width=8, fig.height=4}
dat_orth_coefs_t%>%
  left_join(dat_alloy,
                        by = "alloy_rep_id")%>%
  filter(alloy %in% c("NbV","V","Nb"))%>%
  mutate(rep = factor(rep))%>%
  ggplot(aes(x=Nb,
             y = val))+
  geom_point(aes(color= rep))+
  facet_wrap(~coef_names,
             scales = "free")+
  theme_bw()
```

```{r}


out_dat_t <- dat_orth_coefs_t%>%
              pivot_wider(names_from = "coef_names",
                          values_from = "val")%>%
              left_join(dat_alloy,
                        by = "alloy_rep_id")%>%
                ungroup()

export(out_dat_t,
       file =here::here("Results",
                        "ss_all_ort_coefs_t_uns.csv"))

out_dat_c <- dat_orth_coefs_c%>%
              pivot_wider(names_from = "coef_names",
                          values_from = "val")%>%
              left_join(dat_alloy,
                        by = "alloy_rep_id")%>%
                ungroup()

export(out_dat_c,
       file =here::here("Results",
                        "ss_all_ort_coefs_c_uns.csv"))
```

```{r}
all.equal(out_dat_t$log_max_stress,
          out_dat_c$log_max_stress)
```

```{r}
pnt <- out_dat_t%>%
  filter(Experiment==19)

pnt <- as.matrix(pnt[1,12:16])
X <- as.matrix(out_dat_t[,12:16])
dd <- rdist::cdist(pnt,X, metric = "manhattan")
```


```{r}
out_dat_t%>%
  mutate(Experiment = ifelse(Experiment < 15,0, Experiment),
         Experiment = factor(Experiment),
         dd = as.vector(dd))%>%
  #filter(Experiment!=19)%>%
  ggplot(aes(x= dd,
             y = log_max_strain,
             color = Experiment))+
  geom_point()+
  scale_color_brewer(palette = "Paired")+
  theme_bw()
  
```



### GAM

```{r}
model_t  = bam(stress ~ 0 + 
                 scaled_strain:alloy_rep_id + 
                 s(scaled_strain,
                           by = alloy_rep_id,
                           bs = "cr",
                           k = 4,
                   sp = 0), 
               data = ss_dat_t_filtered,
               method = 'REML' )

```



```{r}
alloy_rep_id_v <- unique(ss_dat_t_filtered$alloy_rep_id)
```


```{r}
ss_dat_t_filtered %>%
  mutate(pred= model_t$fitted.values)%>%
  filter(alloy_rep_id %in% alloy_rep_id_v[c(1,12,17,19,20)])%>%
  ggplot(aes(x = scaled_strain,
             group = alloy_rep_id,
             color = alloy))+
  geom_point(aes(y = stress),
             alpha = 0.2,
             shape =16)+
  geom_line(aes(y = pred),
            linewidth =1)+
  theme_bw()+
  theme(legend.position = "bottom")

```

```{r}
ss_dat_c %>%
  filter(alloy %in% c("NbV","Nb_V","V","Nb"),
         strain < 0.15)%>%
  unite("alloy_rep_id", 
        c("alloy_id", "rep"),
        remove = F)%>%
  mutate(Nb = factor(Nb))%>%
  ggplot(aes(x = strain,
             group = alloy_rep_id,
             color = Nb))+
  geom_line(aes(y = stress),
            linewidth =1)+
  scale_color_brewer(palette = "Dark2")+
  theme_bw()+
  labs(title = "NbV Compression")+
  theme(legend.position = "left")

```


```{r}
basis_coefs_t <- coef(model_t)
#basis_coefs

dat_coefs_t <- tibble(names = names(basis_coefs_t),
                    values= unname(basis_coefs_t))

head(dat_coefs_t)
```



```{r}
model_c  = bam(stress ~ 0 + scaled_strain:alloy_rep_id + 
                 s(scaled_strain,
                           by = alloy_rep_id,
                           bs = "cr",
                           k = 4), 
               data = ss_dat_c_filtered,
               method = 'REML' )


```









```{r}
ss_dat_c_filtered%>%
  filter(alloy == "NbV")%>%
  ggplot(aes(x = scaled_strain,
             group = rep_f,
             color = rep_f))+
  geom_line(aes(y = stress))+
  theme_bw()+
  facet_wrap(~Nb)+
  labs(title = "NbV")+
  theme(legend.position = "bottom")
```



```{r}

ss_dat_c_filtered %>%
  mutate(pred= model_c$fitted.values)%>%
  ggplot(aes(x = scaled_strain,
             group = alloy_rep_id,
             color = alloy_id))+
  geom_point(aes(y = stress),
             alpha = 0.1,
             shape =16)+
  geom_line(aes(y = pred),
            linewidth =1)+
  theme_bw()+
  theme(legend.position = "none")

```




###Extracting coefficients from the model,
```{r}



basis_coefs_c <- coef(model_c)
#basis_coefs

dat_coefs_c <- tibble(names = names(basis_coefs_c),
                    values= unname(basis_coefs_c))

head(dat_coefs_c)
```




###export in csv(need to do it using console, to avoid repeatation every time),

write.csv(dat_coefs_t, file= "dat_coefs_t_not_ordered.csv")
write.csv(dat_coefs_c, file= "dat_coefs_c_not_ordered.csv")


### Extract basis and export

```{r}
source(here::here("utilities.R"))
```


```{r}
df_coefs_t <- mod_all_coefs_to_df_fun(mod = model_t,
                                  ss_dat_sort = ss_dat_t_filtered)

df_coefs_c <- mod_all_coefs_to_df_fun(mod = model_c,
                                  ss_dat_sort = ss_dat_c_filtered)
```





```{r}
dat_alloy <- ss_dat_c_filtered%>%
                          arrange(alloy_rep_id)%>%
                          group_by(alloy_rep_id)%>%
                          slice_head(n=1)%>%
            ungroup()%>%
            select(alloy_rep_id,alloy,Mo,Nb,Ta,V,W, rep)
```


```{r}
df_coefs_t%>%
  left_join(dat_alloy,
                        by = "alloy_rep_id")%>%
  filter(alloy %in% c("NbV","V","Nb"))%>%
  mutate(rep = factor(rep))%>%
  ggplot(aes(x=Nb,
             y = val))+
  geom_point(aes(color= rep))+
  facet_wrap(~coef_names,
             scales = "free")+
  theme_bw()
```


```{r}
out_dat_t <- df_coefs_t%>%
              pivot_wider(names_from = "coef_names",
                          values_from = "val")%>%
              left_join(dat_alloy,
                        by = "alloy_rep_id")

export(out_dat_t,
       file =here::here("Results",
                        "ss_all_coefs_t.csv"))

out_dat_c <- df_coefs_c%>%
              pivot_wider(names_from = "coef_names",
                          values_from = "val")%>%
              left_join(dat_alloy,
                        by = "alloy_rep_id")

export(out_dat_c,
       file =here::here("Results",
                        "ss_all_coefs_c.csv"))
```

###importing the ordered coefficients,
```{r}

ord_coefs_t = read.csv("ordered_coefs_t.csv")
ord_coefs_c = read.csv("ordered_coefs_c.csv")


```


*******
dat_intercepts <- dat_coefs[1:21,]

dat_intercepts <- dat_intercepts%>%
                  separate(names,
                           sep = "alloy(.*)",
                           into = c("alloy"))%>%
                  mutate(coef_type = "Intercept")


dat_smooth_coefs <- dat_coefs[-c(1:21),]


dat_smooth_coefs <- dat_smooth_coefs%>%
                    pivot_wider(names_from = names,
                                values_from = values)%>%
                    pivot_longer(cols = starts_with("s"),
                                 values_to = "values",
                                 names_to = c("ignore","alloy","coef_type"),
                             names_pattern = "s(scaled_strain):alloy(.*).(.)")

******* 








